Log or not - Analysis of ECDC forecasts

### 2022-11-21 analysis/Analysis ECDC forecasts.Rmd
update plots

## Basic data summary
```{r}
hub_data |>
  summarise(min_date = min(forecast_date), 
            max_date = max(forecast_date)) |>
  mutate(week_diff = (max_date - min_date - 1) / 7)

@@

## Figure 5 - Correlations between everything
```{r}
wis_vs_total <- function(scores, summary_fct = mean, fulldata = hub_data) {

@@

## Change of average scores for increasing forecast horizons

```{r}
scores |> 
  filter(model == "EuroCOVIDhub-ensemble") |>
  group_by(scale, target_type, horizon) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = horizon)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(scale ~ target_type) + 
  theme_scoringutils() + 
  labs(x = "Forecast horizon in weeks", y = "Multplicative change in interval score")

ggsave("output/figures/HUB-scores-over-horizon.png", width = 7, height = 4)

@@

## Figure 6 - Look at pairwise comparisons and changes in rankings

@@

plot_ranking_change <- summarised_pairwise |>
  select(model, scale, relative_skill) |>
  group_by(scale) |>
  mutate(rank = rank(-relative_skill), 
         x = ifelse(scale == "natural", 0.4, 2.8), 
         x_arrow = ifelse(scale == "natural", 1.7, 2.7)
         ) |>
  group_by(model) |>
  mutate(color = ifelse(diff(relative_skill) > 0, "deteriorated", "not deteriorated")) |>
  ggplot(aes(y = rank, x = x, group = model, label = model)) +
    geom_path(
      aes(x=x_arrow, color = color), 
      arrow = arrow(length = unit(0.09,"npc")), 
      lineend = "round", linejoin = "mitre",
      size=1, show.legend = FALSE) +
  # geom_text(size=3.3, hjust = 0) +
  coord_cartesian(#xlim = c(0.5, 4), 
                  ylim = c(0.8, 9.15)) +
  theme_scoringutils() +
  theme(axis.title = element_blank(),
        axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(), 
        legend.position="none")

@@

return(
  list(
    plot_ranking_change, plot_rel_skill_natural, plot_rel_skill_log, plot_diffs, plot_rel_wis
  )
)

plot_ranking_change + plot_rel_skill + plot_diffs + plot_rel_wis + #plot_distr_scores 
  plot_layout(design = layout) +
  plot_layout(heights = c(1, 2)) +
  plot_layout(widths = c(2, 1, 2)) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
}

@@

@@

## Figure 7 - Example comparisons of forecasts on the log and the natural scale

put_plot_together("EuroCOVIDhub-ensemble")
ggsave(filename = "output/figures/HUB-model-comparison-ensemble.png", width = 9, height = 7)

put_plot_together("epiforecasts-EpiNow2")
ggsave(filename = "output/figures/HUB-model-comparison-epinow.png", width = 9, height = 7)

put_plot_together("EuroCOVIDhub-baseline", locationname = "DE")
ggsave(filename = "output/figures/HUB-model-comparison-baseline.png", width = 9, height = 7)

>>>>

@@

## =============================================================================
## Figure 5 - Correlations between everything
```{r}
wis_vs_total <- function(scores, summary_fct = mean, fulldata = hub_data) {

@@

## =============================================================================
## Figure 6 - Example comparisons of forecasts on the log and the natural scale

put_plot_together("EuroCOVIDhub-ensemble")
ggsave(filename = "output/figures/HUB-model-comparison-ensemble.png", width = 10, height = 7)

put_plot_together("epiforecasts-EpiNow2")
ggsave(filename = "output/figures/HUB-model-comparison-epinow.png", width = 10, height = 7)

put_plot_together("EuroCOVIDhub-baseline", locationname = "DE")
ggsave(filename = "output/figures/HUB-model-comparison-baseline.png", width = 10, height = 7)

@@

## =============================================================================
## Figure 7 - Look at pairwise comparisons and changes in rankings (plus Appendix figures)

@@

plot_ranking_change <- summarised_pairwise |>
  select(model, scale, relative_skill) |>
  group_by(scale) |>
  mutate(rank = rank(-relative_skill), 
         x = ifelse(scale == "natural", 0.4, 2.8), 
         x_arrow = ifelse(scale == "natural", 1.7, 2.7)
         ) |>
  group_by(model) |>
  mutate(color = ifelse(diff(relative_skill) > 0, "deteriorated", "not deteriorated")) |>
  ggplot(aes(y = rank, x = x, group = model, label = model)) +
    geom_path(
      aes(x=x_arrow, color = color), 
      arrow = arrow(length = unit(0.09,"npc")), 
      lineend = "round", linejoin = "mitre",
      size=1, show.legend = FALSE) +
  # geom_text(size=3.3, hjust = 0) +
  coord_cartesian(#xlim = c(0.5, 4), 
                  ylim = c(0.75, 8.25)) +
  theme_scoringutils() +
  theme(axis.title = element_blank(),
        axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(), 
        legend.position="none")

plot_rel_wis + plot_ranking_change

@@

return(
  list(
    plot_ranking_change, plot_rel_skill_natural, plot_rel_skill_log, plot_diffs, plot_rel_wis
  )
)
}

@@

## =============================================================================
## Summary numbers for the text + Figure Available Forecasts fo Appendix

```{r}
hub_data |>
  summarise(min_date = min(forecast_date), 
            max_date = max(forecast_date)) |>
  mutate(week_diff = (max_date - min_date - 1) / 7)

## =============================================================================
## Summary table for Appendix

@@
